---
title: "Alcohol vs Seat choice"
author: "Chi N"
date: "summer2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```
The box for the back rows are much larger than the front and the middle seats.The red dots th outlers are shown above each box. The differnce in the sizes will be ran with the series of t.test's two at a time to show the significance. 
## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=davisdata)
```
the number of people who sat in the back row was 32. The front row contained 33 people, and the middle had the larges amount with 83. 

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
the inferential test shows that the probability is too low, at 0.000110. We reject the null hypothesis as is.
```{r}
#we specify the margins starting at the bottom and proceeding clockwise - thus 8.7 is the left side margin to hold the names of the factors
par(mar = c(3, 8.7, 2, 2))
plot(TukeyHSD(model1),las=2)
```


A mutiple comparison test showcases a subtantal difference or a lack of using each pair of data. the comparison of the middle row and the front had little to no differnce to each other. This is shown by the (a) broken line, this bracket is placed where this broken line is and explain there is no difference in data. The middle and back seats are on the right portion of the graph and show a negative result, based on the bottom line, placing it at approximately -11.The front and the back portion of the graph are compared and showed the most significant change in numberial data. The bracket is in the negative numbers, at around -13. this inference explains the most drinking was done in the back row. 

## Conclusions



